Topological Equivariant Artist Model

### 2021-12-29 slides/main.tex
sheaves morphism

\begin{frame}{Morphism on Sheaves:\onslide<5-6,8-|handout:5-6,8->{ pullback}\onslide<8-|handout:8->{ and }\onslide<7-|handout:7->{pushforward}}
    \begin{equation*}
        \begin{tikzcd}[ampersand replacement=\&, row sep=huge]
            \onslide*<7-|handout:7->{\sheafc_{\gbasec}(\gbasec)} 
            \onslide*<7-|handout:7->{\arrow[rr, "\textcolor{functor}{\vindexpush}", color=functor]} \& \& 
            \onslide*<7-|handout:7->{(\textcolor{functor}{\vindexpush}\sheafc_{\gbasec})(\dbasec)}  \\
            \onslide*<2-|handout:2->{\gbasec}
            \onslide*<3-|handout:3->{\arrow[rr, "\vindex", color=functor]}
            \onslide*<7-|handout:7->{\arrow[u, "\sheaf_{\gbasec}", color=sheaf]}
            \onslide*<6,8-|handout:6,8->{\arrow[d, dashed, color=sheaf]} \&  \& 
            \onslide*<1-|handout:1->{\dbasec}
            \onslide*<4-6,8-|handout:4-6,8->{\arrow[d, "\sheaf_{\dbasec}", color=sheaf]}
            \onslide*<7-|handout:7->{\arrow[u, dashed, color=sheaf]} \\
            \onslide*<5-6,8-|handout:5-6,8->{(\textcolor{functor}{\vindexpull}\sheafc_{\dbasec})(\gbasec)} 
            \onslide*<5-6,8-|handout:5-6,8->{\arrow[rr, "\textcolor{functor}{\vindexpull}", color=functor]}  \& \& 
            \onslide*<4-6,8-|handout:4-6,8->{\sheafc_{\dbasec}(\dbasec)}                             
        \end{tikzcd}
    \end{equation*}
\end{frame}

>>>>

\begin{frame}{
\only<-8|handout:-8>{Morphism on Sheaves:}
\only<5-6|handout:5-6>{pullback}\only<7|handout:7>{pushforward} 
\only<8|handout:8>{pullback \& pushforward}\only}
    \begin{equation*}
        \begin{tikzcd}[ampersand replacement=\&, row sep=huge]
            \onslide*<7-|handout:7->{\sheafc_{\gbasec}(\gbasec)} 
            \onslide*<7-|handout:7->{\arrow[rr, "\textcolor{functor}{\vindexpush}", color=functor]} \& \& 
            \onslide*<7-|handout:7->{(\textcolor{functor}{\vindexpush}\sheafc_{\gbasec})(\dbasec)}  \\
            \onslide*<2-|handout:2->{\gbasec}
            \onslide*<3-|handout:3->{\arrow[rr, "\vindex", color=functor]}
            \onslide*<7-|handout:7->{\arrow[u, "\sheaf_{\gbasec}", color=sheaf]}
            \onslide*<6,8-|handout:6,8->{\arrow[d, dashed, color=sheaf]} \&  \& 
            \onslide*<1-|handout:1->{\dbasec}
            \onslide*<4-6,8-|handout:4-6,8->{\arrow[d, "\sheaf_{\dbasec}", color=sheaf]}
            \onslide*<7-|handout:7->{\arrow[u, dashed, color=sheaf]} \\
            \onslide*<5-6,8-|handout:5-6,8->{(\textcolor{functor}{\vindexpull}\sheafc_{\dbasec})(\gbasec)} 
            \onslide*<5-6,8-|handout:5-6,8->{\arrow[rr, "\textcolor{functor}{\vindexpull}", color=functor]}  \& \& 
            \onslide*<4-6,8-|handout:4-6,8->{\sheafc_{\dbasec}(\dbasec)}                             
        \end{tikzcd}
    \end{equation*}
\end{frame}

\begin{frame}{\only<1-3:handout:1-3>{Pullback \& Pushforward are Isomorphic}\only<4-|handout:4>{Data to Graphic is a Sheaf Morphism}}
    \begin{equation*}
        \begin{tikzcd}[ampersand replacement=\&]
          \onslide*<1-|handout:1->{\sheafc_{\gbasec}(\gbasec)} 
          \onslide*<1-3|handout:1-3>{\arrow[rr, "\textcolor{functor}{\vindexpush}", color=functor]}  
          \onslide*<4-|handout:4->{\arrow[rr, "\vindexpushc", color=artist]} 
          \& \& 
          \onslide*<1-|handout:1->{(\textcolor{functor}{\vindexpush}\sheafc_{\gbasec})(\dbase)} \\
          \& \& \\
          \onslide*<1-|handout:1->{(\textcolor{functor}{\vindexpull}\sheafc_{\dbase})(\gbasec)}
          \onslide*<1-3|handout:1-3>{\arrow[rr, "\textcolor{functor}{\vindexpull}", color=functor]}
          \onslide*<4-|handout:4->{\arrow[rr, "\vindexpullc", color=artist]}
          \onslide*<2-3|handout:2-3>{\arrow[uu, "\textcolor{homset}{hom_{\gbasec}}", color=homset]} 
          \onslide*<4-|handout:4->{\arrow[uu, "\vartistc_{\vindexpushc}", color=artist]}
          \&  \& 
          \onslide*<1-|handout:1->{\sheafc_{\dbase}(\dbase)} 
          \onslide*<2-3|handout:2-3>{\arrow[uu, "\textcolor{homset}{hom_{\dbasec}}"', color=homset]}
          \onslide*<4-|handout:4->{\arrow[uu, "\vartistc_{\vindexpullc}"', color=artist]}
          \onslide*<3|handout:3>{\arrow[lluu, "\textcolor{homset}{hom_{\dbasec,\gbasec}}"' description, dashed, color=homset]}
          \onslide*<4-|handout:4->{\arrow[lluu, "\vartistc"' description, dashed, color=artist]}
        \end{tikzcd}
      \end{equation*}

    \onslide<3|handout:3>{
        \begin{equation*}
        \textcolor{homset}{hom}_{\gbasec}(\textcolor{functor}{\vindexpull}\sheafc_{\dbase}, \sheafc_{\gbasec}) = 
    \textcolor{homset}{hom}_{\dbase}(\sheafc_{\dbase}, \textcolor{functor}{\vindexpush}\sheafc_{\gbasec})
        \end{equation*}
    }
    \onslide<4|handout:4>{
        \begin{equation*}
            \vartistc_{\vindexpull} = \vartistc_{\vindexpush}
        \end{equation*}
    }
\end{frame}

\begin{frame}{}
